Near Optimal Behavior with Approximate State Abstraction

### 2016-02-04 paper/results_discussion.tex
revamped intro, results, background a bit

\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.png}
}
\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.png}
}

>>>>

\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_num_abstract_states.pdf}
}
\subfigure[NChain]{
\includegraphics[width=0.46\columnwidth]{figures/nchain_epsilon_vs_value_of_abstract_policy_init_ground_state.pdf}
}
